Graph Generators: State of the Art and Open Challenges

### 2019-07-17 generators_general.tex
merged 3.5 with 3.1; Tables I and II updated

>>>>

\paragraph{HPC Scalable Graph Analysis Benchmark} The HPC Scalable Graph
Analysis Benchmark~\cite{HPCgraph,Bader:2005:DIH:2099301.2099360} consists of a
weighted, directed graph that has a power-law distribution and four related
analysis techniques (namely graph construction, graph extraction with BFS,
                     classification of large vertex sets, and graph analysis
                     with betweenness centrality). The generator has the
following parameters: the number of nodes, the number of edges, and maximum weight of
an edge. It outputs a list of tuples containing identifiers of vertices of an
edge (with the direction from the first one to the second one) and weights
(positive integers  with a uniform random distribution) assigned to the edges of
the multigraph.  The algorithm of the generator is based on R-MAT. 
%To reduce the data
%locality, the vertex ids are randomly permuted and the output
%tuples are shuffled. A related project from the same authors
%developed for the 9th DIMACS Shortest Paths Challenge is GTgraph~\cite{GTgraph}.
%t involves three types of graphs: (1) Erd\"{o}s-R\'{e}nyi random graphs, (2)
%different graphs from the DARPA HPCS SSCA\#2 graph theory benchmark
%(version 1.0), and (3) small-world graphs generated using the R-MAT graph
%generator.
